### 2015-01-16 fundamentals/examples.tex
some language to explain why this section is in the demonstration section.

The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and growth via its
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simulation 
results for both once-through and more complex recycling scenarios demonstrate that 
\Cyclus possesses the fundamental fuel cycle simulation capabilities to 
contribute to the field.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

%** full-system plutonium buildup for open
\TODO{(no recycle), modified open, and closed (infinite-pass recycle)
variations of}
%the scenario described above (all just a single reactor).  **

>>>>

The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven development paradigm. Additionally, simulation 
results for both once-through and more complex recycling scenarios demonstrate that 
\Cyclus possesses the fundamental fuel cycle simulation capabilities to 
contribute to the field.

@@

The \Cyclus community-driven software development model seeks to break the unproductive cycle proliferating overspecialized simulators and 
to leverage the collective expertise of fuel cycle researchers. Through the 
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@
